---
title: "future on ARC R server"
author: "Ruben Arslan"
date: "30 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Future package

```{r load}
# vignette("future-1-overview")
library(future)
```

## Simple, local

A simple local example. Multiprocess starts whatever multiprocess tool is available on the platform (e.g. Multicore on Unix-based system, PSOCK cluster on Windows).
```{r}
plan(multiprocess)
v %<-% {
 cat("Resolving...\n")
 3.14
}
v
```

## Remote ARC R server (no scheduler)

This approach works for a server that is SSH-accessible and has R installed. To be able to SSH in without storing your password in plaintext somewhere, you'll need to set up public key authentification. You do this by copying your public key to `~/.ssh/authorized_keys` on the server. If you've already generated a public key on your local machine, it should be in `~/.ssh/id_rsa.pub` or something similar. If you haven't yet, Google how :-)
You'll have to do this for every server you want to use.

```{r}
library("future") # this is the package we use to flexibly scale our processing
library("listenv") # this is a helper package that allows us to assign the results to a list even if they come in at different times

## Set up access to remote login node
login <- tweak(remote, workers = "arslan@arc-srv-cpt7.mpib-berlin.mpg.de") # Your username goes before the @
plan(login) # this tells the future package that we want to use a remote server for running our future operations

# but maybe the reason we want to shift to a server is not that we want to run a simple sequential operation there.
# maybe we want to take advantage of parallelisation and run the operation in parallel on multiple cores
## Specify future topology
## login node -> { cluster nodes } -> { multiple cores }
plan(list(
  login,
  multicore,
  sequential
))
# demo("mandelbrot", package = "future", ask = FALSE)


## (a) This will be evaluated on the cluster login computer
x %<-% { # this operator binds the result of the promise/future to x
  thost <- Sys.info()[["nodename"]]
  tpid <- Sys.getpid()
  y <- listenv()
  for (task in 1:4) {
    ## (b) This will be evaluated on a different core
    y[[task]] %<-% {
      mhost <- Sys.info()[["nodename"]]
      mpid <- Sys.getpid()
      z <- listenv()
      for (jj in 1:2) {
        ## (c) this will be evaluated sequentially on the same core
        z[[jj]] %<-% data.frame(task = task,
                                top.host = thost, top.pid = tpid,
                                mid.host = mhost, mid.pid = mpid,
                                host = Sys.info()[["nodename"]],
                                pid = Sys.getpid())
      }
      Reduce(rbind, z)
    }
  }
  Reduce(rbind, y)
}

print(x)
```


