---
title: "future on Leipzig R server"
author: "Ruben Arslan"
date: "30 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Future package

```{r load}
# vignette("future-1-overview")
library(future)
```

## Simple, local

A simple local example. Multiprocess starts whatever multiprocess tool is available on the platform (e.g. Multicore on Unix-based system, PSOCK cluster on Windows). By using `%<-%` instead of `<-` we use `future`.

```{r}
plan(multisession)
v %<-% {
 cat("Resolving...\n")
 3.14
}
v
```

## Remote Leipzig R server (no scheduler)

### SSH ID
This approach works for a server that is SSH-accessible and has R installed. To be able to SSH in without storing your password in plaintext somewhere, you'll need to set up public key authentification. You do this by copying your public key to `~/.ssh/authorized_keys` on the server. If you've already generated a public key on your local machine, it should be in `~/.ssh/id_rsa.pub` or something similar. 

#### Steps
Enter the following in the Terminal/command line of your local computer. If you already have an SSH key, skip this:

```shell
ssh-keygen
```

Now, run
```shell
ssh-copy-id YOURUSERNAME@rstudio03.sc.uni-leipzig.de
```

Enter your password. Try if it worked:

```shell
ssh YOURUSERNAME@rstudio03.sc.uni-leipzig.de
```

If you're not prompted for your password, you're good to go!


### Send a brms model to the server
For this to work, you need the future and the brms package to be installed on the server and locally.

```{r}
library(future) # this is the package we use to flexibly scale our processing
library(brms)

## Set up access to remote login node
plan(cluster, workers = rep("xb629fypu@rstudio03.sc.uni-leipzig.de", 3)) # this tells the future package that we want to use a remote server for running our future operations and would run at most 3 models in parallel
v %<-% {
 cat("Resolving...\n")
 3.14
}
v

prior1 <- prior(normal(0,10), class = b) +
  prior(cauchy(0,2), class = sd)

fit1 %<-% brm(count ~ zAge + zBase + Trt + (1|patient),
            data = epilepsy, # you don't need to upload the data to the server first 
            family = poisson(), 
            file = "fit1", # smart to save the result as a file name so you can later quickly retrieve an already fitted model. you have to change this name for every new model
            file_refit = "on_change", # don't use the cached version if model or data changed,
            cores = 4, # always make use of between-chain parallelisation on the server
            prior = prior1)

fit2 %<-% brm(count ~ zAge + zBase * Trt + (1|patient),
            data = epilepsy, # you don't need to upload the data to the server first 
            family = poisson(), 
            file = "fit2", # smart to save the result as a file name so you can later quickly retrieve an already fitted model. you have to change this name for every new model
            file_refit = "on_change", # don't use the cached version if model or data changed,
            cores = 4, # always make use of between-chain parallelisation on the server
            prior = prior1) %seed% TRUE
```

As you'll see when you run this code, it immediately returns. Only when we "use" the variables later on, do we have to wait for the result from the server.

```{r}
fit1
fit2
```



